Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-11 paper/disc20clustering.tex
Consistency

In this section, we consider the learning variant of Dynamic Balanced Graph Partitioning.
For this setting, we show a surprisingly high lower bound of $\Omega(k \cdot \ell)$.
The lower bound can be easily translated to the partitioning model (studied in Section~\ref{sec:part}) with a~finite request sequence.
At the end of this section, we discuss an asymptotically optimal upper bound.

>>>>

In this section, we consider the learning variant of dynamic balanced graph partitioning problem.
For this setting, we show a surprisingly high lower bound of $\Omega(k \cdot \ell)$.
The lower bound holds also in the general partitioning model (studied in Section~\ref{sec:part}).
At the end of this section, we discuss an asymptotically optimal upper bound for the learning variant.
